MCMC convergence diagnostics

### 2023-01-15 src/naomi-simple_compare/comparison.Rmd
Start thinking about how to calculate the PSIS: basically we just want to put all the samples into tmb$fit$obj$fn(), get the NLL, difference them, then use the loo package
Add orderly details about the runs we compare

@@

@@

>>>>

We compare the inference results from `TMB`, `aghq` and `tmbstan`.
Import these inference results as follows:

@@

For more information about the conditions under which these results were generated, see:

```{r}
depends <- yaml::read_yaml("orderly.yml")$depends

for(i in seq_along(depends)) {
  report_name <- names(depends[[i]])
  print(paste0("Inference results obtained from ", report_name, " with the query ", depends[[i]][[report_name]]$id))
  report_id <- orderly::orderly_search(query = depends[[i]][[report_name]]$id, report_name)
  print(paste0("Obtained report had ID ", report_id, " and was run with the following parameters:"))
  print(orderly::orderly_info(report_id, report_name)$parameters)
}
```

@@

Suppose we have two sets of samples from the posterior.
For each sample we are going to want to evaluate the log-likelihood, so that we can calculate the log-likelihood ratios.
We can extract the `TMB` objective function for the log-likelihood as follows:

```{r}
tmb$fit$obj$fn()
```
